Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-01-07 Manuscript/TEM_draft.tex
Updates on the method part
Structure:
-Individual effects of missing data parameters
-Combined effect of missing data parameters

%Part 1
As the amount of missing data in the morphological part of the total evidence matrix increases, our ability to recover the "best" tree's topology decreases, regardless of the missing data parameter ($M_{L}$, $M_{F}$ or $M_{C}$), the method of tree inference (Maximum Likelihood or Bayesian) or the tree comparison metric used (Normalised Robinson-Foulds or Normalised Triplets distance). However, the different missing data parameters and tree inference methods do not affect the topology in the same way (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}). In any combination of parameters or metrics, the Maximum Likelihood bootstraps trees and the Bayesian posterior distribution trees performs in a substantially similarly (Table ~\ref{Tab_Results-Difference_methods}) and worth than the Maximum Likelihood and the Bayesian consensus trees (Fig.~\ref{Fig_Results-permeth_perparam} - see discussion). %add discussion link

%Part 2
\subsection{Individual effects of missing data parameters} 
As the amount of missing data increases across all three parameters, the ability to recover the "best" tree's topology decreases (Fig.~\ref{Fig_Results-permeth_perparam}). However, the decrease of the Normalised Robinson-Fould distance plateaus at minimum of 0.69 for Bayesian consensus tree (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam} - see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values) and there is no substantial difference in topological recovery for 50\% or 75\% of missing living taxa (upper triangle in Fig.~\ref{Fig_Results-paircomp_within}-A). Therefore, clades seems to be more conserved in the Bayesian consensus tree more than any other method (see discussion).  %add discussion link
On the other hand, the decrease in Normalised Triplets distance is less contrasted with a greater overlap of Normalised Triplets distance with the Maximum Likelihood tree (Fig.~\ref{Fig_Results-permeth_perparam}) - mean Bhattacharrya Coefficient=0.10 for the Normalised Robinson-Foulds distance and 0.61 for the Normalised Triplets distance - see table ~\ref{Tab_Results-Difference_methods}).

%Part 3
\subsection{Effect of missing data for fossil taxa ($M_{F}$)}
As the amount of missing data in the fossil part of the matrix increases, the ability to recover the "best" tree's topology decreases as well (Fig.~\ref{Fig_Results-permeth_perparam}). For the Robinson-Fould distance, we observe the same pattern than for $M_{L}$ with a better topological recovery of the Bayesian consensus trees on any other methods (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}). However, the Normalised Triplets distance drops drastically when going from 25\% of missing data to 50\% (mode) %get the modal values here
making this parameter more sensible to wildcard taxa in the Bayesian consensus tree (Fig.~\ref{Fig_Results-permeth_perparam} - see discussion). %add discussion link

%Part 4
\subsection{Effect of missing character ($M_{C}$)}
As described for the two previous parameters $M_{L}$ and $M_{F}$, an increase in the amount of missing characters decreases the ability to recover the "best" tree's topology decreases (Fig.~\ref{Fig_Results-permeth_perparam}). Similarly again, the Bayesian consensus trees shows higher Normalised Robinson-Fould distance than the Maximum Likelihood tree (Fig.~\ref{Fig_Results-permeth_perparam}). And in a similar way as for the $M_{F}$ parameter, the Normalised Triplet distance drops drastically when going from 25\% of missing data to 50\% (mode). %get the modal values here

%Part 5
\subsection{Combined effect of missing data parameters ($M_{L}$, $M_{F}$ and $M_{C}$)} 
The combine of the missing data parameters ($M_{L}$, $M_{F}$ and $M_{C}$) reduces the ability to recover the "best" tree's topology when each parameters contains a maximum of missing data (i.e. $M_{L}$=75\%, $M_{F}$=75\% and $M_{C}$=75\% - Fig.~\ref{Fig_Results-global_perparam} and see \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the combined effects of the parameters in both Normalised Robinson-Foulds and Normalised Triplets distance for the Maximum Likelihood Bootstraps trees and the Bayesian posterior trees distribution). Regarding the clade conservation (i.e. the Normalised Robinson-Foulds distances), the Bayesian consensus tree greatly outperforms the Maximum likelihood trees with Normalised Robinson-Foulds scores always superior than 0.69 (Fig.~\ref{Fig_Results-global_perparam} - see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the exact values) regardless the combination of missing data parameters (Fig.~\ref{Fig_Results-paircomp_within}-A). However, for the Normalised Triplets distance, the Bayesian consensus tree often displays negative values (i.e. differences greater than expected by chance) but with few substantial differences (Fig.~\ref{Fig_Results-paircomp_within}-B). Also the differences between the Normalised scores of the Maximum Likelihood trees and Bayesian consensus trees are substantially difference for the Normalised Robinson-Foulds distance (mean Bhattacharrya Coefficient=0.10) and for the Normalised Triplets distance (mean Bhattacharrya Coefficient=0.61 - see table ~\ref{Tab_Results-Difference_methods}). Thus the sensitivity of the Bayesian consensus trees to wild card taxa is not highly different than the one for the Maximum likelihood trees (i.e. the distribution of Normalised Triplets distance have a high probability of overlap). The results of the probability of overlap between the pairwise distributions of Normalised Robinson-Foulds and Triplets distances of the Maximum Likelihood trees, the Maximum Likelihood Bootstrap trees and the Bayesian posterior trees distribution is available in the \hyperref[SupplementaryMaterial]{Supplementary Material Section 3}.

%Binned removed bits from former results.

%As the amount of missing data in the morphological part of the total evidence matrix increases, our ability to recover the "best" tree's topology decreases, regardless of the missing data parameter ($M_{L}$, $M_{F}$ or $M_{C}$), the method of tree inference (Maximum Likelihood or Bayesian) or the tree comparison metric used (Normalised Robinson-Foulds or Normalised Triplets distance). 
%However, the different missing data parameters and tree inference methods do not affect the topology in the same way (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}). % And figure 3 too right? TG: Yep
%The Normalised Robinson-Foulds distance calculate for the trees inferred in Maximum Likelihood framework decreases with the increase of missing data in our three parameters ($M_{L}$, $M_{F}$ or $M_{C}$) with a modal Normalised Robinson-Fould score always below 0.5 when 75\% of the living taxa have no data ($M_{L}$=75\% - Fig.~\ref{Fig_Results-global_perparam}). However, in Bayesian inference, the ability of the method (the Bayesian consensus tree) to recover a "best" tree's topology plateaus at a minimal Normalised Robinson-Fould score of 0.69 (Fig.~\ref{Fig_Results-global_perparam} - see \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the values distribution). The results of the topological recovery with the parameters combination in both Normalised Robinson-Foulds and Triplets distances for the Maximum Likelihood bootstrap trees and the Bayesian posterior distribution trees are available in the \hyperref[SupplementaryMaterial]{Supplementary Material Section 3}.
%All parameters combinations are different than the "best" tree (always red) in both metrics.
%The lowest probability of overlap (low Bhattacharrya Coefficient values) between pairwise distributions of parameters combinations ($M_{L}$, $M_{F}$ and $M_{C}$ with 0\%, 10\%, 25\%, 50\% or 75\% missing data) is always between the comparison of Normalised distance (Robinson-Foulds or Triplets) of the "missing data" tree with no missing data ($M_{L}$=0\%, $M_{F}$=0\% and $M_{C}$=0\%) and all the other "missing data" trees.
%The parameters combinations are less dissimilar in Triplets than in RF (less red).
%However, pairwise comparisons are more dissimilar (low Bhattacharrya Coefficient values) in the Normalised Robinson-Fould distance results than in the Normalised Triplets distance results.
%The ML parameter (0% and 10%) are more different in RF and Triplets (red stripes at the base). The ML parameter (50, 75) are the more similar (green upper part) in RF.
%The Normalised Robinson-Fould distance for the comparisons between the trees with a low amount of missing data for the living taxa ($M_{L}$=0\% and 10\%) shows the most dissimilarities with the other parameter combinations.
%The combination of the ML parameter (0% and 10%) and the MC parameter (0, 10, 25) are the most different (details on the red stripes).
%Check supplementary for the rest
%The results of the probability of overlap between the pairwise distributions of Normalised Robinson-Foulds and Triplets distances of the Maximum Likelihood trees, the Maximum Likelihood Bootstrap trees and the Bayesian posterior trees distribution is available in the \hyperref[SupplementaryMaterial]{Supplementary Material Section 3}.
%When looking at the pairwise Bhattacharyya Coefficients between all the parameters combinations for Bayesian consensus trees, % NC: Instead just state the result. "We found that number of missing living taxa ($M_{L}$) results the lowest probabilities of overlap (table X)". In the same way as you wouldn't say "Using a linear regression we found that x ~ Y." You'd say "X and Y were significantly correlated (Table1)".
%NC: Also what IS the result really? You find that ML overlaps less with the other parameters so it's significantly different in it's effect? And from the graph you can see it's worse? What does oerlap MEAN in terms of the answer to the question, i.e. how do the parameters affect topological recovery. 
%the number of missing living taxa ($M_{L}$) results the lowest probabilities of overlap (right lower corner in Fig.~\ref{Fig_Results-paircomp_within}-A). However, when looking at the Triplets distance, because of the high overlap in confidence intervals, there is no major region with low probability of overlap. One should note however that the bottom line of the matrix where the Bhattacharyya Coefficients are very low is due to comparing the distribution of the pairwise comparison of the "best" tree against the "missing-data" tree with no missing data ($M_{L}$=0\%, $M_{C}$=0\%, $M_{F}$=0\%) , leading to a normalised Triplets score of 1 every time (with no variance, see Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}). The pairwise comparisons for the other methods (Maximum Likelihood, Bootstraps and Bayesian posterior trees) are available in the supplementary materials (see \hyperref[SupplementaryMaterial]{Supplementary Material Section 3}).
%NC: I'd start by describing the pattern with reference to figs 2 and 3 and then the "significant" results
%When looking at the comparisons between the methods 
%using the Robinson-Foulds distance, the Bayesian consensus trees have the least overlap with respectively the Bayesian posterior trees and the Bootstrap (Fig.~\ref{Fig_Results-paircomp_without}-A). Using the Triplets distance, the two methods that have the most distribution %NC: ???
%are the Bootstraps and the Bayesian posterior trees (Fig.~\ref{Fig_Results-paircomp_without}-B). These results are due to the difference in comparing topologies between Maximum Likelihood and Bayesian consensus trees and Bootstraps and Bayesian posterior trees: the latter two are based on a random pairwise comparison of a sub-sample of 1000 trees. This is likely to add noise to the data.

@@

Our results show that the ability to recover the "best" tree's topology in a Total Evidence framework decreases with increasing missing data, regardless of how data were removed or the method of tree inference used. However, these factors affected topological recovery in different ways and to different extents. 
Decreasing the overall number of morphological characters in the matrix ($M_{C}$) and the amount of living taxa with morphological data ($M_{L}$) had worst effects on topological recovery (Fig.~\ref{Fig_Results-paircomp_within}). Additionally, using Bayesian consensus trees recovered the "best" tree's topology more consistently than using Maximum Likelihood trees or Bayesian posterior trees distributions (Fig.~\ref{Fig_Results-global_perparam} and Fig.~\ref{Fig_Results-paircomp_within}).
% ----->
% NC: Probably needs another summing up line here. Or maybe not
% <-----
% NC: Make sure it's parameters then tree building methods. NC: Make sure the order of the parameters is always the same L,F, C or whatever! THROUGHOUT the paper. Also correct RF and T to standardised OR normalised RF and T.
% NC: Might want to add a couple of subheadings to match those in the results.
As proposed in previous studies, our results show that the amount of missing data is not a problem \textit{per se} for Total Evidence methods, as long as enough morphological characters overlaps for most taxa in the matrix \citep[e.g.][]{kearneyfragmentary2002,wiensmissing2003,rouresite-specific2011,pattinsonphylogeny2014}. % NC: What do you mean by data overlap here? That species have overlapping characters?

@@

%Methods
%Part saying the difference between ML and Baycon
When using the Normalised Robinson-Foulds distance to measure topological similarity, the Bayesian consensus trees recover the "best" tree's topology more often than Maximum Likelihood trees (Fig.~\ref{Fig_Results-global_perparam}). In fact, regardless of the amount of missing data, Bayesian consensus trees always displays the highest Normalised Robinson-Foulds score (always $>$ 0.69; see \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for details). However, regarding the Normalised Triplets distance, the topological similarity with the "best" tree's topology decreases in the same way for both the Maximum Likelihood trees and the Bayesian consensus trees (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}).
%Part saying the difference between BS and baytrees
Regardless of the metric, the Maximum Likelihood boostrap trees and the Bayesian posterior trees distribution always performed poorlier in their ability to recover the "best" tree's topology, even when no morphological data was missing ($M_{L}$=0\% - Fig.~\ref{Fig_Results-permeth_perparam}). This reflects the fact it is difficult to compare two distributions of trees, and each comparison between a set of "missing data" tree and "best" tree in these cases involved 1000 random pairwise comparisons rather than just one. This will obviously add noise to the results for these two methods.

@@

%Discussing results 2
%   -Why is Baycon so different than Baytre? Since Baycon is calculated from Baytre.
Also, in the case of the lower performances of the Bayesian consensus trees when using the Triplets distance, one can note the high overlap of the confidence intervals (Fig. ~\ref{Fig_Results-permeth_perparam} and Fig. ~\ref{Fig_Results-paircomp_within}-B). % NC: Don't get the relevance of the last sentence/why it fits here. Can you expand?
% NC: Probably want some  statement here about bayesian being better than ML, and if you want to fix a single topology in TE we recommend a bayesian consensus. If you want to account for tree uncertainty we recommend a bayesian posterior distribution. Our results dont suggest this is bad, but more suggest that we can't compare trees very well in this case.

% $§4: Thus, baycon seems the best way to go >...
% ^§5: >... but we have to take into account problems in our protocol.

%\label{metrics_discussion}
%This difference between the metrics can be explained by their respective ability to measure the differences between two trees \citep{kuhnerpractical2014}. As shown in Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}, the contrast between the results of the two metrics can be explained by the actual nature of both metrics (see \hyperref[SupplementaryMaterial]{Supplementary Material S2}):
%\begin{enumerate}
%\item{The Robinson-Foulds metric is a conservative metric, which is more sensible to single taxon displacement because it will count clades as similar only if they are composed of the same taxa with the same topologies \citep{RF1981}. When getting closer to the root of the tree, displacement of single taxon makes the clades not being exactly identical any more even if the clade still contains all the other taxa in both trees. This metric illustrates therefore the conservation of clades among the compared trees (i.e. when the normalised Robinson-Foulds distance is close to 1, most of the clades in the two trees are identical).}
%\item{On the other hand, the Triplets method is measuring the position of each taxon towards two other reference taxa \citep{critchlowthe1996}. It will penalise only trees when taxa get removed furthest from their original position. This metric therefore illustrates the amount of wildcard taxa \citep{kearneyfragmentary2002} between the two compared trees (i.e. when the score is closed to 1, few wildcard taxa are present in the tree).}
%\end{enumerate}
%Therefore, in our study, both metrics are showing two different aspects of tree topology. For example, regarding the Bayesian consensus trees, completes clade are conserved most of the time (Fig.~\ref{Fig_Results-global_perparam}-top) but with an increasing amount of missing data, wildcard taxa get more and more displaced (Fig.~\ref{Fig_Results-global_perparam}-bottom). Because we are comparing the Baysian consensus tree to a single tree topology, the probability of recovering the exact position of a wildcard taxa than in the "best" tree is really low and even reducing with the amount of missing data. Regarding this fundamental differences, the Robinson-Foulds metric performs better in showing a distance from the true topology than the Triplets distance \citep{kuhnerpractical2014}. Therefore, the results for the Bayesian consensus trees can be preferred on the Maximum Likelihood trees because - when using the Robinson-Fould distance - they display a higher ability to recover the "best" tree's topology (Fig. ~\ref{Fig_Results-permeth_perparam}).

@@

% $§6: Knowing the caveats, we can try to fix them >...
% ^§7: >... by taking into account data realness (fossil templates and rate heterogeneity).

%§7
%Further directions - is that necessary though?
% NC: Cut for now, might want to put these ideas in the appropriate places above instead.
%   -Using real data
%One way to address this issue 
% NC: Which issue???
%would be to run a similar analysis using real data. The amount of studies using Total Evidence data type matrices is steadily increasing \citep[e.g.][]{ronquista2012,slaterphylogenetic2013,beckancient2014} and one could analysis these total evidence matrices in the same framework as this study. However, the true topology (obtained from a matrix with no missing data) is unlikely to be known. A second way to address this issue, and especially to incorporate the variation of signal in morphological character would be to simulate morphological characters at different rates \citep{wrightbayesian2014} or to apply patterns of missing data directly obtained from the fossil record \citep{pattinsonphylogeny2014}. Nevertheless, our simulation already show clear results of the effect of missing data on topology in a Total Evidence framework. Also, our results show how recovering the "best" tree's topology can be improved by using Bayesian consensus trees in combination with a maximum amount of characters and a of living taxa with morphological data.
%   -Looking at branch length?

% $§7: But despite the caveats above, missing data is not a big deal >...
% ^§8: >... We can use TEM for integrating fossils into trees.

%§8
%Back to the importance of TEM - How we can use fossils (Intro-§2)
%   -Data is not a major problem
%Despite the various caveats discussed above, we answered our main question on how does Total Evidence matrices perform in recovering topology with different methods and different amounts of missing data.
% NC: For a concluding paragraph, don't start by reminding people of the caveats! End strongly and confidently
% Also no need to restate the question - instead give the answer.
%   -Good and promising method.
%Our results shows that this method performance decreases mainly with a reduction in the overlap of morphological data. To address this problem, we propose to increase the data overlap by coding living species and to have a large morphological matrix. Also, our results shows disparity among methods and a clear superiority %NC: Not really 
%of the Bayesian consensus tree topology over the Maximum Likelihood one.

>>>>

%Part 1
%increase in missing data leads to decrease in topological recovery no matter what
As the amount of missing data in the morphological part of the Total Evidence matrix increases, our ability to recover the "best" tree's topology decreases, regardless of the missing data parameter ($M_{L}$, $M_{F}$ or $M_{C}$), the tree inference method (Maximum Likelihood or Bayesian) or the tree comparison metric used (Normalised Robinson-Foulds or Normalised Triplets distance). However, the different missing data parameters and tree inference methods do not affect the topology in the same way (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}).
%bootstrap and bayesian treesets are always worst bad
In any combination of missing data parameters or topological distance metrics, the Maximum Likelihood bootstraps trees and the Bayesian posterior tree distribution performs substantially similarly (Median Bhattacharrya Coefficient between both tree inference methods using Normalised Robinson-Foulds distance or Normalised Triplets distance is respectively 0.85 and 0.96 - see Table ~\ref{Tab_Results-Difference_methods}) and worth than the Maximum Likelihood trees and the Bayesian consensus trees (Fig.~\ref{Fig_Results-permeth_perparam} - see discussion %add discussion link
 and also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the effect of the combined parameters on the Maximum Likelihood bootstraps trees and the Bayesian posterior tree distribution).

%Part 2
\subsection{Individual effects of missing data parameters}
%Individually, increase in missing data leads to decrease in topological recovery as well
As the amount of missing data increases across all three parameters, our ability to recover the "best" tree's topology decreases (Fig.~\ref{Fig_Results-permeth_perparam}).
%Differences between MaxLik and Baycon in RF
The Normalised Robinson-Foulds distance is always substantially lower for the Maximum Likelihood %(minimum Normalised Robinson-Foulds distance for $M_{L}$, $M_{F}$ and $M_{C}$ of respectively @, @ and @) %minimum RF value for each parameter individually% TG: or useless (just Bhattacharrya)?
 trees than for the Bayesian consensus trees %(minimum Normalised Robinson-Foulds distance for $M_{L}$, $M_{F}$ and $M_{C}$ of respectively @, @ and @)  %minimum Tr value for each parameter individually% TG: or useless (just Bhattacharrya)?
(Bhattacharrya Coefficient between the methods for $M_{L}$, $M_{F}$ and $M_{C}$ of respectively @, @ and @  %BC value for each parameter individually between both methods RF
- Fig.~\ref{Fig_Results-permeth_perparam} upper and see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values).
%Differences between MaxLik and Baycon in Tr
However, the Normalised Triplets distance is similar between the Maximum Likelihood trees and the Bayesian consensus trees for the $M_{L}$ parameter (Bhattacharrya Coefficient between both tree inference methods for $M_{L}$ = @ %BC value for ML between both methods
- Fig.~\ref{Fig_Results-permeth_perparam} lower and see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values); for the two other parameters $M_{F}$ and $M_{C}$, the Normalised Triplets distance is substantially higher for the Maximum Likelihood trees than for the Bayesian consensus trees (Bhattacharrya Coefficient between both tree inference methods for $M_{F}$ and $M_{C}$ of respectively @ and @  %BC value for each parameter individually between both methods Tr
- Fig.~\ref{Fig_Results-permeth_perparam} lower and see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values).

%Part 3
\subsection{Combined effect of missing data parameters ($M_{L}$, $M_{F}$ and $M_{C}$)} 
%Combined, increase in missing data leads to decrease in topological recovery as well
The combined effect of the missing data parameters ($M_{L}$, $M_{F}$ and $M_{C}$) reduces the ability to recover the "best" tree's topology when each parameters contains a maximum of missing data (i.e. $M_{L}$=75\%, $M_{F}$=75\% and $M_{C}$=75\% - Fig.~\ref{Fig_Results-global_perparam} and see \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the combined effects of the parameters in both Normalised Robinson-Foulds and Normalised Triplets distance for the Maximum Likelihood Bootstraps trees and the Bayesian posterior trees distribution).
%Differences between MaxLik and Baycon in RF
As described above, The Normalised Robinson-Foulds distance is higher for the Bayesian consensus trees topologies than for the Maximum Likelihood trees topologies with a median Normalised Robinson-Foulds distance for the Bayesian consensus trees and for the Maximum likelihood trees of respectively @ and @ % Median RF value for Baycon and MaxLik
(Fig.~\ref{Fig_Results-global_perparam} upper - see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values).
%Differences between MaxLik and Baycon in Tr
The Normalised Triplets distance is lower for the Bayesian consensus trees topologies than for the Maximum Likelihood trees topologies with a median Normalised Triplets distance for the Bayesian consensus trees and for the Maximum likelihood trees of respectively @ and @ % Median Tr value for Baycon and MaxLik
(Fig.~\ref{Fig_Results-global_perparam} lower - see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values).
%Significance
However, the Normalised Robinson-Foulds distances are substantially less similar between the Bayesian Consensus trees and the Maximum Likelihood trees than the Normalised Triplets distances (Median Bhattacharrya Coefficient between both tree inference methods for the Normalised Robinson-Foulds distance and the Normalised Triplets distance is respectively 0.10 and 0.61 - Fig.~\ref{Fig_Results-global_perparam} and table~\ref{Tab_Results-Difference_methods}).

%And now the combined effect of parameters in RF for the Baycon trees
Regarding the effect of the combination of our missing data parameters on the ability to recover the "best" tree's topology, using both Normalised Robinson-Foulds and Normalised Triplets distances from the Bayesian consensus trees, the parameter combination with no missing data (i.e. $M_{L}$ = 0\%, $M_{F}$ = 0\%, $M_{C}$ = 0\%) is always the most dissimilar to all the other parameters combination (red %change color
 line at the bottom of Fig.~\ref{Fig_Results-paircomp_within} A and B). However, the Normalised Robinson-Foulds distance displays more dissimilarities than the Normalised Triplets distance (the median Bhattacharrya coefficient among all pairwise missing data parameters combinations from the Bayesian consensus trees using the Normalised Robinson-Foulds and the Normalised Triplets distance are respectively @ and @ %value for median BC from pairwise comp in Baycon-RF and Baycon-Tr
 Fig.~\ref{Fig_Results-paircomp_within} - see also \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for the table of values). Additionally, when using the Normalised Robinson-Foulds distance, there is no dissimilarity between the trees with 50\% and 75\% of missing living taxa ($M_{L}$) and any other combination of parameter state for the two other missing data parameters $M_{F}$ and $M_{C}$ (e.g.. $M_{L}$ = 50\%, $M_{F}$ = 0\%, $M_{C}$ = 10\%; or $M_{L}$ = 50\%, $M_{F}$ = 75\%, $M_{C}$ = 50\%; etc) as well as for the trees with 50\% and 75\% of missing characters ($M_{C}$) and any other combination of parameter state for the two other missing data parameters $M_{L}$ and $M_{F}$ (Fig.~\ref{Fig_Results-global_perparam} upper and Fig.~\ref{Fig_Results-paircomp_within}-A).

@@

Our results show that the ability to recover the "best" tree's topology in a Total Evidence framework decreases with increasing amount of missing data, regardless of how data were removed or the method of tree inference used. However, these factors affected topological recovery in different ways and to different extents. 
Decreasing the overall number of morphological characters in the matrix ($M_{C}$) and the amount of living taxa with morphological data ($M_{L}$) had worst effects on topological recovery (Fig.~\ref{Fig_Results-paircomp_within}). Additionally, using Bayesian consensus trees recovered the "best" tree's topology more consistently than using Maximum Likelihood trees or Bayesian posterior trees distributions (Fig.~\ref{Fig_Results-global_perparam} and Fig.~\ref{Fig_Results-paircomp_within}).
% ----->
% NC: Probably needs another summing up line here. Or maybe not
% <-----
% NC: Make sure it's parameters then tree building methods. NC: Make sure the order of the parameters is always the same L,F, C or whatever! THROUGHOUT the paper. Also correct RF and T to standardised OR normalised RF and T.
% NC: Might want to add a couple of subheadings to match those in the results.
As proposed in previous studies, our results show that the amount of missing data is not a problem \textit{per se} for Total Evidence methods, as long as enough morphological characters overlaps for most taxa in the matrix \citep[e.g.][]{kearneyfragmentary2002,wiensmissing2003,rouresite-specific2011,pattinsonphylogeny2014}. % NC: What do you mean by data overlap here? That species have overlapping characters?

@@

%Methods
%Part saying the difference between ML and Baycon
When using the Normalised Robinson-Foulds distance to measure topological similarity, the Bayesian consensus trees recover the "best" tree's topology more often than Maximum Likelihood trees (Fig.~\ref{Fig_Results-global_perparam}). In fact, regardless of the amount of missing data, Bayesian consensus trees always displays the highest Normalised Robinson-Foulds score (always $>$ 0.69; see \hyperref[SupplementaryMaterial]{Supplementary Material Section 3} for details). However, regarding the Normalised Triplets distance, the topological similarity with the "best" tree's topology decreases in the same way for both the Maximum Likelihood trees and the Bayesian consensus trees (Fig.~\ref{Fig_Results-permeth_perparam} and Fig.~\ref{Fig_Results-global_perparam}).

%Part saying the difference between BS and baytrees
Regardless of the metric, the Maximum Likelihood boostrap trees and the Bayesian posterior trees distribution always performed poorlier in their ability to recover the "best" tree's topology, even when no morphological data was missing ($M_{L}$=0\% - Fig.~\ref{Fig_Results-permeth_perparam}). This reflects the fact it is difficult to compare two distributions of trees, and each comparison between a set of "missing data" tree and "best" tree in these cases involved 1000 random pairwise comparisons rather than just one. This will obviously add noise to the results for these two methods.

@@

@@
